---
title: "Creating new layouts"
author: "RTE"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating new layouts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `antaresViz` package allows to visualize simulation results. Several default
layouts are available in the package, but, in some cases, the user will need to
create a custom layout.

In this vignette we illustrate how to create a custom layout along the German
inner borders.

```{r setup, message=FALSE, warning=FALSE}
library(antaresViz)
library(dplyr)
library(rnaturalearth)
library(ggplot2)
library(sf)
```


The coordinates of administratives regions of most countries can be found in the
`rnaturalearth` package. Grouping these regions together often allows to obtain
the desired layout. For instance:

```{r}
germany <- rnaturalearth::ne_states(
  geounit = "germany",
  returnclass = "sf"
)

german_zones <- germany %>% 
  select(iso_3166_2, geometry) %>% 
  transmute(zone = case_when(
    iso_3166_2 %in% c("DE-SL", "DE-RP", "DE-NW", "DE-HE") ~ "34_DE",
    iso_3166_2 %in% c("DE-BW", "DE-BY") ~ "35_DE",
    iso_3166_2 %in% c("DE-NI", "DE-HH", "DE-HB", "DE-SH") ~ "36_DE",
    TRUE ~ "37_DE"
  )) %>% 
  group_by(zone) %>% 
  summarise()

ggplot(german_zones) +
  geom_sf(aes()) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


```


Then the layout `map` can be generated from `german_zones` with a single line of
code:

```{r}
map <- as(st_transform(german_zones, crs = 4326), "Spatial")
```

This `map` is then used to generate a `mapLayout` object:

```{r, eval=FALSE}
zone_layout <- list(
  coords = coords,
  links = links,
  map = map,
  all_coords = coords
)
class(zone_layout) <- "mapLayout"
attr(zone_layout, "type") <- "areas"
```


